---
title: "Vehicle Choice App"
author: "NHartley"
date: "2024-03-02"
output:
  ioslides_presentation: default
  beamer_presentation: default
---

```{css, echo=FALSE}
/* Adjust font size for all text */
body, p, li, td, th {
  font-size: 70%; /* Set to 70% of the original size */
}


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## OVERVIEW

-   The goal of this app is for users to highlight eligible cars from the mtcars data set by toggling two variables
-   1: transmission type (manual vs. automatic)
-   2: Miles per Gallon (mpg)

## INSTRUCTIONS

-   1: Select choice of transmission type with the radio button
-   2: Select mpg threshold using the slider
-   3: Click "Submit"

## SUMMARY STATISTICS OF MTCARS DATA SET: R CODE BLOCK

```{r echo = TRUE, eval = FALSE}
# Load the mtcars dataset
data(mtcars)

# Rename columns with more descriptive names
colnames(mtcars) <- c("Car_Name", "MPG", "Cylinders", "Displacement", 
                      "Horsepower", "Weight", "Acceleration", "Model_Year", 
                      "Origin", "Transmission")

# Remove columns "Car_Name", "Origin", "Model_Year", "NA"
mtcars_filtered <- mtcars[, !colnames(mtcars) %in% c("Car_Name", "Origin", 
                                                     "Model_Year", NA)]

# Apply summary function to the modified dataset
summary(mtcars_filtered)

```

## SUMMARY STATISTICS OF MTCARS DATA SET: OUTPUT

```{r echo = FALSE, eval = TRUE}
# Load the mtcars dataset
data(mtcars)

# Rename columns with more descriptive names
colnames(mtcars) <- c("Car_Name", "MPG", "Cylinders", "Displacement", "Horsepower", 
                      "Weight", "Acceleration", "Model_Year", "Origin", "Transmission")

# Remove columns "Car_Name", "Origin", "Model_Year", and any columns with NA values
mtcars_filtered <- mtcars[, !colnames(mtcars) %in% c("Car_Name", "Origin", "Model_Year", NA)]

# Apply summary function to the modified dataset
summary(mtcars_filtered)

```

## BOXPLOT OF FUEL EFFICIENCY BASED ON TRANSMISSION TYPE: R CODE BLOCK

```{r echo=TRUE, eval=FALSE}
# Load the mtcars dataset
data(mtcars)
# Filter the dataset for manual and automatic transmissions
mtcars_manual <- mtcars[mtcars$am == 1, ]
mtcars_automatic <- mtcars[mtcars$am == 0, ]
# Create a boxplot comparing mpg for manual and automatic transmissions
boxplot(mpg ~ am, data = mtcars, 
        main = "MPG Comparison by Transmission Type",
        xlab = "Transmission Type",
        ylab = "Miles Per Gallon",
        col = c("blue", "red"),
        names = c("Automatic", "Manual"))
```

## BOXPLOT OF FUEL EFFICIENCY BASED ON TRANSMISSION TYPE: OUTPUT

```{r echo=FALSE, eval = TRUE}
# Load the mtcars dataset
data(mtcars)
# Filter the dataset for manual and automatic transmissions
mtcars_manual <- mtcars[mtcars$am == 1, ]
mtcars_automatic <- mtcars[mtcars$am == 0, ]
# Create a boxplot comparing mpg for manual and automatic transmissions
boxplot(mpg ~ am, data = mtcars, 
        main = "MPG Comparison by Transmission Type",
        xlab = "Transmission Type",
        ylab = "Miles Per Gallon",
        col = c("blue", "red"),
        names = c("Automatic", "Manual"))
```

## LINEAR MODEL: R CODE BLOCK
```{r echo=TRUE, EVAL = FALSE}
# Fit a linear regression model
model <- lm(mpg ~ wt + cyl + as.factor(am), data = mtcars)
# Plot the observed vs. fitted values
plot(mtcars$mpg, fitted(model), xlab = "Observed MPG", ylab = "Fitted MPG", main = "Observed vs. Fitted MPG (using Weight, Cylinders and Trans. type")
# Add a reference line with slope 1 (ideal fit)
abline(a = 0, b = 1, col = "red")
```

## LINEAR MODEL: OUTPUT

```{r echo=FALSE, EVAL = TRUE}
# Fit a linear regression model
model <- lm(mpg ~ wt + cyl + as.factor(am), data = mtcars)
# Plot the observed vs. fitted values
plot(mtcars$mpg, fitted(model), xlab = "Observed MPG", ylab = "Fitted MPG", main = "Observed vs. Fitted MPG (using Weight, Cylinders and Trans. type")
# Add a reference line with slope 1 (ideal fit)
abline(a = 0, b = 1, col = "red")
```
